Supplementary Information

### 2021-06-03 doc/manuscript/ForestGEO_treerings_SI.Rmd
updated knit
First knit with updated repo name

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
#READING IN TABLES TO GET STATS FOR TEXT
path_to_dir <- dirname(dirname(getwd())) # get path to repo (ForestGEO-climate-sensitivity)

# MOVE FIGURE FILES (doing this because I got an error when using the absolute path to call figures)
#traditional comparison
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/traditional_comparison/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/formal_comparison/figures/", "^climwin_vs_dcc_.+[.]png$", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/traditional_comparison/")

# climwin plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/climwin_plots_combined/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climwin_plots_combined/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/climwin_plots_combined/")

#composite plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/composite_plots/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/composite_plots/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/composite_plots/")

#decadal plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/decadal_plots/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/tree-rings_global-change/decadal_plots/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/decadal_plots/")

#recruitment plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/recruitment_years/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO_dendro/data_processed/", "^Recrutement_years_.+[.]png$",  full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/recruitment_years/")

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
#READING IN TABLES TO GET STATS FOR TEXT
path_to_dir <- dirname(dirname(getwd())) # get path to repo (ForestGEO-tree-rings)

# MOVE FIGURE FILES (doing this because I got an error when using the absolute path to call figures)
#traditional comparison
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/traditional_comparison/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/results/formal_comparison/figures/", "^climwin_vs_dcc_.+[.]png$", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/traditional_comparison/")

# climwin plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/climwin_plots_combined/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/results/climwin_plots_combined/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/climwin_plots_combined/")

#composite plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/composite_plots/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/results/composite_plots/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/composite_plots/")

#decadal plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/decadal_plots/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/tree-rings_global-change/decadal_plots/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/decadal_plots/")

#recruitment plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/recruitment_years/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO_dendro/data_processed/", "^Recrutement_years_.+[.]png$",  full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-tree-rings/doc/manuscript/tables_figures/SI_figures/recruitment_years/")
